Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2017-11-14 manuscript-md/03_results.Rmd
Cleanup latest round of results

table_dat <- means_dat %>%
  filter(
    model_type == "hierarchical",
    !(param %in% c("SLA", "leaf_lifespan") & mass_area == "area")
  ) %>%
  mutate(
    mu_lo = if_else(param == "Rdmass", mu_lo * 1000, mu_lo),
    mu_mean = if_else(param == "Rdmass", mu_mean * 1000, mu_mean),
    mu_hi = if_else(param == "Rdmass", mu_hi * 1000, mu_hi),
    lo_f = formatC(mu_lo, digits = 3),
    mid_f = formatC(mu_mean, digits = 3),
    hi_f = formatC(mu_hi, digits = 3),
    value = sprintf("%s (%s,%s)", mid_f, lo_f, hi_f),
    value = if_else(grepl("Vcmax|Jmax", param) & pft == "C4G", "---", value)
  ) %>%
  select(pft, param, value) %>%
  mutate(
    param = factor(param, both_params) %>% 
      forcats::lvls_revalue(param_markdown_nounit[both_params]),
  )%>%
  spread(param, value) %>%
  arrange(pft)

@@

plot_dat <- means_dat %>%
  mutate(
    #too_few = sample_size < 2,
    #mu_hi = if_else(too_few, NA_real_, mu_hi),
    #mu_lo = if_else(too_few, NA_real_, mu_lo),
    #mu_mean = if_else(too_few, NA_real_, mu_mean),
    irrelevant = grepl("Vcmax|Jmax", param) & pft == "C4G",
    mu_hi = if_else(irrelevant, NA_real_, mu_hi),
    mu_lo = if_else(irrelevant, NA_real_, mu_lo),
    mu_mean = if_else(irrelevant, NA_real_, mu_mean),
    ## TODO: Fix these in the prior and re-run
    mu_hi = pclip(param, "Vcmax_mass", mu_hi, 1.5),
    mu_hi = pclip(param, "Vcmax_area", mu_hi, 100),
    mu_hi = pclip(param, "Jmax_mass", mu_hi, 1.8),
    mu_hi = pclip(param, "Jmax_area", mu_hi, 150),
    mu_mean = pclip(param, "Jmax_area", mu_mean, 150),
    mu_hi = pclip(param, "Rdmass", mu_hi, 0.03),
    mu_hi = pclip(param, "Rdarea", mu_hi, 0.0035),
    mu_mean = pclip(param, "Rdarea", mu_mean, 0.0035),
    mu_lo = pclip(param, "Rdarea", mu_lo, 0.0035),
    mu_hi = pclip(param, "Parea", mu_hi, 0.285),
    #mu_lo = pclip(param, "Jmax_area", mu_lo, 40, FALSE),
    param = forcats::lvls_revalue(param, param_fancy_chr[both_params])
  )

@@

```{r boxprep}
hier_mass_file <- "../output/hier.mass.clm45.NA.2017-11-13-1250.rds"
hier_area_file <- "../output/hier.area.clm45.NA.2017-11-13-1312.rds"
multi_mass_file <- "../output/multi.mass.clm45.NA.2017-11-13-1231.rds"
multi_area_file <- "../output/multi.area.clm45.NA.2017-11-13-1245.rds"

>>>>

censor <- function(rxp, pft, pfts, param, value) {
  if_else(grepl(rxp, param) & pfts %in% pft, "---", value)
}

table_dat <- means_dat %>%
  filter(
    model_type == "hierarchical",
    !(param %in% c("SLA", "leaf_lifespan") & mass_area == "area")
  ) %>%
  mutate(
    mu_lo = if_else(param == "Rdmass", mu_lo * 1000, mu_lo),
    mu_mean = if_else(param == "Rdmass", mu_mean * 1000, mu_mean),
    mu_hi = if_else(param == "Rdmass", mu_hi * 1000, mu_hi),
    mu_lo = if_else(param == "Rdarea", mu_lo * 1000, mu_lo),
    mu_mean = if_else(param == "Rdarea", mu_mean * 1000, mu_mean),
    mu_hi = if_else(param == "Rdarea", mu_hi * 1000, mu_hi),
    lo_f = formatC(mu_lo, digits = 3),
    mid_f = formatC(mu_mean, digits = 3),
    hi_f = formatC(mu_hi, digits = 3),
    value = sprintf("%s (%s,%s)", mid_f, lo_f, hi_f),
    value = censor("Vcmax|Jmax", "C4G", pft, param, value),
    value = censor("Rdmass", "ShDBo", pft, param, value),
    value = censor("Jmax_mass", c("NlEBo", "NlD"), pft, param, value),
    value = censor("Jmax_area", c("NlD"), pft, param, value)
  ) %>%
  select(pft, param, value) %>%
  mutate(
    param = factor(param, both_params) %>% 
      forcats::lvls_revalue(param_markdown_nounit[both_params]),
  )%>%
  spread(param, value) %>%
  arrange(pft)

@@

plot_dat <- means_dat %>%
  mutate(
    #too_few = sample_size < 2,
    #mu_hi = if_else(too_few, NA_real_, mu_hi),
    #mu_lo = if_else(too_few, NA_real_, mu_lo),
    #mu_mean = if_else(too_few, NA_real_, mu_mean),
    irrelevant = grepl("Vcmax|Jmax", param) & pft == "C4G",
    mu_hi = if_else(irrelevant, NA_real_, mu_hi),
    mu_lo = if_else(irrelevant, NA_real_, mu_lo),
    mu_mean = if_else(irrelevant, NA_real_, mu_mean),
    ## TODO: Fix these in the prior and re-run
    mu_hi = pclip(param, "Vcmax_mass", mu_hi, 1.5),
    mu_hi = pclip(param, "Vcmax_area", mu_hi, 100),
    mu_hi = pclip(param, "Jmax_mass", mu_hi, 1.8),
    mu_hi = pclip(param, "Jmax_area", mu_hi, 150),
    mu_mean = pclip(param, "Jmax_area", mu_mean, 150),
    mu_hi = pclip(param, "Rdmass", mu_hi, 0.03),
    mu_mean = pclip(param, "Rdmass", mu_mean, 0.03),
    mu_lo = pclip(param, "Rdmass", mu_lo, 0.03),
    mu_hi = pclip(param, "Rdarea", mu_hi, 0.0025),
    mu_mean = pclip(param, "Rdarea", mu_mean, 0.0025),
    mu_lo = pclip(param, "Rdarea", mu_lo, 0.0025),
    mu_hi = pclip(param, "Parea", mu_hi, 0.285),
    #mu_lo = pclip(param, "Jmax_area", mu_lo, 40, FALSE),
    param = forcats::lvls_revalue(param, param_fancy_chr[both_params])
  )

@@

```{r boxprep}
outdir <- "../output"
hier_mass_file <- tail(dir(outdir, "hier.mass.clm45", full.names = TRUE), 1)
hier_area_file <- tail(dir(outdir, "hier.area.clm45", full.names = TRUE), 1)
multi_mass_file <- tail(dir(outdir, "multi.mass.clm45", full.names = TRUE), 1)
multi_area_file <- tail(dir(outdir, "multi.area.clm45", full.names = TRUE), 1)
